---
title: "Final project"
author: "Abhishek D Pawar"
date: "1/07/2021"
output: html_document
runtime: shiny
---
# variable
```{r}
#  Variable name dictionary 
        
# hgi -> Hospital General Information
# cad -> Complications and Death
# hai -> Healthcare associated infection
# mhs -> Medical Hospital spending per patient
# oie -> Outpatient Imaging Efficiency
# pvc -> Payment and Value of Care 
# tec -> Timely and effective Care
# hcahps -> Hospital Consumer Assessment of Healthcare Providers and Systems Patient Survey

      # files extension meaning
# _pivot -> pivot table between Facility id and measure id
# _pivot1 -> total average score for each measure is calculated here
# _pivot2 -> provide hospital's general info to measure groups (using facility ID)
# _agg -> Aggregate table by mean for each measure (mean for each Hospital rating)
# _uni -> unique measure id and measure name table for each measure

```


```{r, include=FALSE}
#please set working directory as per the location of data on your pc
#setwd('C:/Users/abhis/Desktop/Masters/masters sem 2/Data analysis using r/term project/data')
```

```{r, include=FALSE}
library(psych)
library(pander)
library(ggpubr)
library(knitr)
library(tidyr)
library(dplyr)
library(readr)
library(emmeans)
library(citr)
library(reshape2)
library(imputeMissings)

```

```{r}
# these are global options which apply to pandoc functions 

# comment to show after a table is split by column
panderOptions('table.continues', '')              

# this is to control how many characters can be printed in a line 
panderOptions('table.split.table', 140)                                          
```

# Hospital_General_Information

```{r}
hgi <- read.csv('Hospital_General_Information.csv')

hgi[ hgi == "Not Available" ] <- NA
```

```{r}
hgi <- hgi %>% select(-contains("footnote"))

hgi <- hgi %>% select(-contains("Count"))
```


```{r}

# Let's thus subset the data to only the acute care hospitals

hgi <- filter(hgi, Hospital.Type == "Acute Care Hospitals")
hgi$Hospital.Type <- factor(as.character(hgi$Hospital.Type))
#table(hgi$Hospital.Type, hgi$Hospital.overall.rating)
```


```{r}
# Overall rating

hgi$Hospital.overall.rating <- as.numeric(hgi$Hospital.overall.rating)
```

```{r}
pandoc.table(head(hgi,5))
```


```{r}
ggplot(data = hgi, aes(x = Hospital.overall.rating)) + geom_histogram(binwidth = 0.5)
```


#below fuction are used to normalise the data

```{r}
normalize <- function(x, na.rm = TRUE) {
    return((x- min(x)) /(max(x)-min(x)))
}
```

```{r}
normalize_mean <- function(x, na.rm = TRUE) {
    return(abs(x- mean(x))/sd(x))
}
```

```{r}
normalize_log <- function(x, na.rm = TRUE) {
    return(abs(log(x)))
}
```


# Timely_and_Effective_Care

```{r}
# Import data from .CSV file

tec <- read.csv('Timely_and_Effective_Care-Hospital.csv')

pandoc.table(head(tec, 5))
```
Structure of TEC
```{r}
str(tec)
```


this will generate a pivot table between Facility id and measure id
```{r}

tec_pivot <- dcast(tec, Facility.ID ~ Measure.ID, value.var="Score")

tec_pivot <- tec_pivot %>% select(-contains("EDV"))

pandoc.table(head(tec_pivot,5))
```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
tec_pivot[ tec_pivot == "Not Available" ] <- NA
tec_pivot[ tec_pivot == "Not Applicable"] <- NA
tec_pivot[,-c(1)] <- sapply(tec_pivot[,-c(1)],as.numeric)
#sapply(tec_pivot, function(x) (sum(is.na(x))*100)/nrow(tec_pivot) )
```

Impute  missing data with median/ mode
```{r}

tec_pivot1 <- impute(tec_pivot, method = "median/mode")
```

Here we find the total average score for TEC measures
```{r} 
tec_pivot1$'TnEC - Avg Score' <- rowSums( tec_pivot1[,2:17] )/ ncol( tec_pivot1[,2:17])

pandoc.table(head(tec_pivot1,5))
```

Merge TEC with HGI to provide hospital's general info to TEC
```{r}
tec_pivot2 <- merge(tec_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(tec_pivot2,5))
```
Generate Aggregate table for TEC by Hospital overall rating
```{r}
tec_agg <- aggregate(tec_pivot2[,2:18], list(Hospital.overall.rating = tec_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(tec_agg,5))
```
Generate unique measure id and measure name table for TEC
```{r}

tec_uni <- tec[!duplicated(t(apply(tec[,c(10,11)], 1, sort))),][,c(10,11)]
pandoc.table(tec_uni[-1,])
```



# Payment_and_Value_of_Care

```{r}
# Import data from .CSV file

pvc <- read.csv('Payment_and_Value_of_Care-Hospital.csv')
#head(tec)
pandoc.table(head(pvc, 5))
```

Structure of PVC
```{r}
str(pvc)
```

```{r}
pandoc.table(head(dcast(pvc, Facility.ID ~ Payment.Measure.ID, value.var="Payment"),5))
```


this will generate a pivot table between Facility id and measure id
```{r}

pvc_pivot <- dcast(pvc, Facility.ID ~ Payment.Measure.ID, value.var="Payment")

```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
pvc_pivot[ pvc_pivot == "Not Available" ] <- NA
pvc_pivot[ pvc_pivot == "Not Applicable"] <- NA
```


Handling currency data so that it can be converted to numeric data
```{r}

pvc_pivot$PAYM_30_AMI<-gsub("\\$","",pvc_pivot$PAYM_30_AMI)

pvc_pivot$PAYM_30_HF<-gsub("\\$","",pvc_pivot$PAYM_30_HF)

pvc_pivot$PAYM_30_PN<-gsub("\\$","",pvc_pivot$PAYM_30_PN)

pvc_pivot$PAYM_90_HIP_KNEE<-gsub("\\$","",pvc_pivot$PAYM_90_HIP_KNEE)

pvc_pivot$PAYM_30_AMI<-gsub(",","",pvc_pivot$PAYM_30_AMI)

pvc_pivot$PAYM_30_HF<-gsub(",","",pvc_pivot$PAYM_30_HF)

pvc_pivot$PAYM_30_PN<-gsub(",","",pvc_pivot$PAYM_30_PN)

pvc_pivot$PAYM_90_HIP_KNEE<-gsub(",","",pvc_pivot$PAYM_90_HIP_KNEE)


pvc_pivot[,-c(1)] <- sapply(pvc_pivot[,-c(1)],as.numeric)

pvc_pivot1 <- impute(pvc_pivot, method = "median/mode")
```

Here we find the average score for PVC measures
```{r}
pvc_pivot1$'PVC - Avg Score' <- rowSums( pvc_pivot1[,2:5] )/ ncol( pvc_pivot1[,2:5])

pandoc.table(head(pvc_pivot1,5))
```


Merge PVC with HGI to provide hospital's general info to it
```{r}
pvc_pivot2 <- merge(pvc_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(pvc_pivot2,5))
```

Generate Aggregate table for PVC by Hospital overall rating
```{r}
pvc_agg <- aggregate(pvc_pivot2[,2:6], list(Hospital.overall.rating = pvc_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(pvc_agg,5))
```

Generate unique measure id and measure name table for PVC
```{r}

pvc_uni <- pvc[!duplicated(t(apply(pvc[,c(9,10)], 1, sort))),][,c(9,10)]
pandoc.table(pvc_uni)
```


# Outpatient_Imaging_Efficiency

```{r}
# Import data from .CSV file
oie <- read.csv('Outpatient_Imaging_Efficiency-Hospital.csv')
#head(tec)
pandoc.table(head(oie, 5))
```
Structure of OIE
```{r}
str(oie)
```

```{r}

pandoc.table(head(dcast(oie, Facility.ID ~ Measure.ID, value.var="Score"),5))
```

this will generate a pivot table between Facility id and measure id
```{r}

oie_pivot <- dcast(oie, Facility.ID ~ Measure.ID, value.var="Score")
```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
oie_pivot[ oie_pivot == "Not Available" ] <- NA
oie_pivot[ oie_pivot == "Not Applicable"] <- NA

#sapply(oie_pivot, function(x) (sum(is.na(x))*100)/nrow(oie_pivot) )
```

Impute  missing data with median/ mode
```{r}

oie_pivot[,-c(1)] <- sapply(oie_pivot[,-c(1)],as.numeric)

oie_pivot1 <- impute(oie_pivot, method = "median/mode")
```

Here we find the total average score for OIE measures
```{r}
oie_pivot1$'OIE - Avg Score' <- rowSums( oie_pivot1[,2:4] )/ ncol(oie_pivot1[,2:4])

pandoc.table(head(oie_pivot1,5))
```

Merge OIE with HGI to provide hospital's general info to OIE
```{r}
oie_pivot2 <- merge(oie_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(oie_pivot2,5))
```

Generate Aggregate table for OIE by Hospital overall rating
```{r}
oie_agg <- aggregate(oie_pivot2[,2:5], list(Hospital.overall.rating = oie_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(oie_agg,5))
```

Generate unique measure id and measure name table for OIE
```{r}

oie_uni <- oie[!duplicated(t(apply(oie[,c(9,10)], 1, sort))),][,c(9,10)]
pandoc.table(oie_uni)
```

# Medicare_Hospital_Spending_Per_Patient

```{r}
# Import data from .CSV file
mhs <- read.csv('Medicare_Hospital_Spending_Per_Patient-Hospital.csv')
#head(tec)
pandoc.table(head(mhs, 5))
```

Structure of MHS
```{r}
str(mhs)
```

this will generate a pivot table between Facility id and measure id
```{r}

pandoc.table(head(dcast(mhs, Facility.ID ~ Measure.ID, value.var="Score"),5))
```

```{r}

mhs_pivot <- dcast(mhs, Facility.ID ~ Measure.ID, value.var="Score")
```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
mhs_pivot[ mhs_pivot == "Not Available" ] <- NA
mhs_pivot[ mhs_pivot == "Not Applicable"] <- NA

#sapply(mhs_pivot, function(x) (sum(is.na(x))*100)/nrow(mhs_pivot) )
```

Impute  missing data with median/ mode
```{r}

mhs_pivot[,-c(1)] <- sapply(mhs_pivot[,-c(1)],as.numeric)

mhs_pivot1 <- impute(mhs_pivot, method = "median/mode")
```


Here we find the total average score for MHS measures
```{r}
mhs_pivot1$'MHS - Avg Score' <- mhs_pivot1$MSPB.1

pandoc.table(head(mhs_pivot1,5))
```

Merge MHS with HGI to provide hospital's general info to MHS
```{r}
mhs_pivot2 <- merge(mhs_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(mhs_pivot2,5))
```

Generate Aggregate table for MHS by Hospital overall rating
```{r}
mhs_agg <- aggregate(mhs_pivot2[,2:3], list(Hospital.overall.rating = mhs_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(mhs_agg,5))
```

Generate unique measure id and measure name table for MHS
```{r}

mhs_uni <- mhs[!duplicated(t(apply(mhs[,c(9,10)], 1, sort))),][,c(9,10)]
pandoc.table(mhs_uni)
```

# Healthcare_Associated_Infections

```{r}
# Import data from .CSV file
hai <- read.csv('Healthcare_Associated_Infections-Hospital.csv')
#head(tec)
pandoc.table(head(hai, 5))
```

Structure of HAI
```{r}
str(hai)
```

this will generate a pivot table between Facility id and measure id
```{r}

pandoc.table(head(dcast(hai, Facility.ID ~ Measure.ID, value.var="Score"),5))
```


```{r}

hai_pivot <- dcast(hai, Facility.ID ~ Measure.ID, value.var="Score")

#removing measure that are not important and can be represented SIR
hai_pivot <- hai_pivot %>% select(-contains("_NUMERATOR"))
hai_pivot <- hai_pivot %>% select(-contains("_ELIGCASES"))
hai_pivot <- hai_pivot %>% select(-contains("_DOPC"))
hai_pivot <- hai_pivot %>% select(-contains("_CIUPPER"))
hai_pivot <- hai_pivot %>% select(-contains("_CILOWER"))



```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
hai_pivot[ hai_pivot == "Not Available" ] <- NA
hai_pivot[ hai_pivot == "Not Applicable"] <- NA

#sapply(hai_pivot, function(x) (sum(is.na(x))*100)/nrow(hai_pivot) )
```

Impute  missing data with median/ mode
```{r}

hai_pivot[,-c(1)] <- sapply(hai_pivot[,-c(1)],as.numeric)

pandoc.table(head(hai_pivot,5))

hai_pivot1 <- impute(hai_pivot, method = "median/mode")
```

```{r}
#hai_pivot1[,2:7] <- sapply(hai_pivot1[,2:7], FUN = normalize)
```

Here we find the total average score for HAI measures
```{r}
hai_pivot1$'HAI - Avg Score' <- rowSums( hai_pivot1[,2:7] )/ ncol(hai_pivot1[,2:7])

pandoc.table(head(hai_pivot1,5))
```

Merge HAI with HGI to provide hospital's general info to HAI
```{r}
hai_pivot2 <- merge(hai_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(hai_pivot2,5))
```

Generate Aggregate table for HAI by Hospital overall rating
```{r}
hai_agg <- aggregate(hai_pivot2[,2:8], list(Hospital.overall.rating = hai_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(hai_agg,5))
```

Generate unique measure id and measure name table for HAI
```{r}

hai_uni <- hai[!duplicated(t(apply(hai[,c(9,10)], 1, sort))),][,c(9,10)]

#we remove these cause they are not important
hai_uni <- hai_uni[!grepl("_CILOWER", hai_uni$Measure.ID),]
hai_uni <- hai_uni[!grepl("_CIUPPER", hai_uni$Measure.ID),]
hai_uni <- hai_uni[!grepl("_DOPC", hai_uni$Measure.ID),]
hai_uni <- hai_uni[!grepl("_ELIGCASES", hai_uni$Measure.ID),]
hai_uni <- hai_uni[!grepl("_NUMERATOR", hai_uni$Measure.ID),]

pandoc.table(hai_uni)
```


# HCAHPS

```{r}
# Import data from .CSV file
hcahps <- read.csv('HCAHPS-Hospital.csv')
#head(tec)
pandoc.table(head(hcahps, 5))
```

Structure of HCAHPS
```{r}
str(hcahps)
```

```{r}

#pandoc.table(head(dcast(hcahps, Facility.ID ~ HCAHPS.Measure.ID, value.var="Patient.Survey.Star.Rating"),5))
```


this will generate a pivot table between Facility id and measure id
```{r}

hcahps_pivot <- dcast(hcahps, Facility.ID ~ HCAHPS.Measure.ID, value.var="Patient.Survey.Star.Rating")

#removing measure that are not important and can be represented Final measure for it
hcahps_pivot <- hcahps_pivot %>% select(-contains("_p"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_D"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_LINEAR_SCORE"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_A"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_SA"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_0_6"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_7_8"))
hcahps_pivot <- hcahps_pivot %>% select(-contains("_9_10"))

```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
hcahps_pivot[ hcahps_pivot == "Not Available" ] <- NA
hcahps_pivot[ hcahps_pivot == "Not Applicable"] <- NA

#sapply(hcahps_pivot, function(x) (sum(is.na(x))*100)/nrow(hcahps_pivot) )
```

Impute  missing data with median/ mode
```{r}

hcahps_pivot[,-c(1)] <- sapply(hcahps_pivot[,-c(1)],as.numeric)

pandoc.table(head(hcahps_pivot,5))

hcahps_pivot1 <- impute(hcahps_pivot, method = "median/mode")
```

Here we find the total average score for HCAHPS measures
```{r}
hcahps_pivot1$'HCAHPS - Avg Score' <- rowSums( hcahps_pivot1[,2:12] )/ ncol(hcahps_pivot1[,2:12])

pandoc.table(head(hcahps_pivot1,5))
```

Merge HCAHPS with HGI to provide hospital's general info to HCAHPS
```{r}
hcahps_pivot2 <- merge(hcahps_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(hcahps_pivot2,5))
```

Generate Aggregate table for HCAHPS by Hospital overall rating
```{r}
hcahps_agg <- aggregate(hcahps_pivot2[,2:13], list(Hospital.overall.rating = hcahps_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(hcahps_agg,5))
```

Generate unique measure id and measure name table for HCAHPS
```{r}

hcahps_uni <- hcahps[!duplicated(t(apply(hcahps[,c(9,10)], 1, sort))),][,c(9,10)]

# removing the unwanted columns from data
hcahps_uni <- hcahps_uni[!grepl("_P", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_D", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_A", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_SA", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_LINEAR_SCORE", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_0_6", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_7_8", hcahps_uni$HCAHPS.Measure.ID),]
hcahps_uni <- hcahps_uni[!grepl("_9_10", hcahps_uni$HCAHPS.Measure.ID),]

pandoc.table(hcahps_uni)
```



# Complications_and_Deaths

```{r}
# Import data from .CSV file
cad <- read.csv('Complications_and_Deaths-Hospital.csv')
#head(tec)
pandoc.table(head(cad, 5))
```

Structure of CAD
```{r}
str(cad)
```

this will generate a pivot table between Facility id and measure id
```{r}

cad_pivot <- dcast(cad, Facility.ID ~ Measure.ID, value.var="Score")

```

Converting missing values to NA for better imputation process
the not applicable part should not be NA 
but for simplification we have taken this decision
```{r}
cad_pivot[ cad_pivot == "Not Available" ] <- NA
cad_pivot[ cad_pivot == "Not Applicable"] <- NA

#sapply(cad_pivot, function(x) (sum(is.na(x))*100)/nrow(cad_pivot) )
```

Impute  missing data with median/ mode
```{r}

cad_pivot[,-c(1)] <- sapply(cad_pivot[,-c(1)],as.numeric)

pandoc.table(head(cad_pivot,5))

cad_pivot1 <- impute(cad_pivot, method = "median/mode")
```

Here we find the total average score for CAD measures
```{r}
cad_pivot1$'CAD - Avg Score' <- rowSums( cad_pivot1[,2:20] )/ncol(cad_pivot1[,2:20])

pandoc.table(head(cad_pivot1,5))
```

Merge CAD with HGI to provide hospital's general info to CAD
```{r}
cad_pivot2 <- merge(cad_pivot1, hgi[,c(1,12)], by.x="Facility.ID", by.y="Facility.ID")

pandoc.table(head(cad_pivot2,5))
```

Generate Aggregate table for CAD by Hospital overall rating
```{r}
cad_agg <- aggregate(cad_pivot2[,2:21], list(Hospital.overall.rating = cad_pivot2$Hospital.overall.rating), mean)

pandoc.table(head(cad_agg,5))
```

Generate unique measure id and measure name table for CAD
```{r}

cad_uni <- cad[!duplicated(t(apply(cad[,c(9,10)], 1, sort))),][,c(9,10)]

pandoc.table(cad_uni)
```






# hospital rating wise

Creating a final data set by merging all the aggregate data of each measure  
this way we get mean values of all attributes in each measure for each hospital star rating
```{r}

Star_Rating_final <- merge(cad_agg, hai_agg, by.x="Hospital.overall.rating", by.y="Hospital.overall.rating")

Star_Rating_final <- merge(Star_Rating_final, Reduce(function(x,y) merge(x = x, y = y, by = "Hospital.overall.rating"), 
       list(hcahps_agg, mhs_agg, oie_agg, pvc_agg, tec_agg)), by.x="Hospital.overall.rating", by.y="Hospital.overall.rating")

```

Here we take only the total average scores for each of the Seven measures for each star rating
```{r}

Star_Rating_final_general <- Star_Rating_final %>% select(contains(c("Hospital.overall.rating","Avg Score")))
pandoc.table(head(Star_Rating_final_general))
```

# hospital wise


Here we merge all the 7 measure group by facility.ID
this holds 67 attributes (from all 7 measures) for each hospital
```{r}
final <- merge(hgi,cad_pivot1, by.x="Facility.ID", by.y="Facility.ID")

final <- merge(final, Reduce(function(x,y) merge(x = x, y = y, by = "Facility.ID"), 
       list(hai_pivot1,hcahps_pivot1, mhs_pivot1, oie_pivot1, pvc_pivot1, tec_pivot1)), by.x="Facility.ID", by.y="Facility.ID")

```



Here we take only the total average scores for each of the seven measures for each hospital
```{r}

final <- impute(final, method = "median/mode")

final_general <- final %>% select(contains(c("Facility.ID","Score")))

final_general <- merge(hgi,final_general, by.x="Facility.ID", by.y="Facility.ID")

final_general <- impute(final_general, method = "median/mode")

pandoc.table(head(final_general))

```

Scaling up/down the data to bring all measures under similar range for better mapping and plotting.
done for both general data sets
```{r}
#final_general[,c(13:19)] <- sapply(final_general[,c(13:19)], FUN = normalize)

final_general[,c(13)] <- final_general[,c(13)]*50
final_general[,c(14)] <- final_general[,c(14)]*1000
final_general[,c(15)] <- final_general[,c(15)]*200
final_general[,c(16)] <- final_general[,c(16)]*500
final_general[,c(17)] <- final_general[,c(17)]*50
final_general[,c(18)] <- final_general[,c(18)]*(3/100)
final_general[,c(19)] <- final_general[,c(19)]*10


```

```{r}
Star_Rating_final_general1 <- Star_Rating_final_general

#Star_Rating_final_general1[,c(2:8)] <- sapply(Star_Rating_final_general1[,c(2:8)], FUN = normalize)

Star_Rating_final_general1[,c(2)] <- Star_Rating_final_general1[,c(2)]*(100/2)
Star_Rating_final_general1[,c(3)] <- Star_Rating_final_general1[,c(3)]*10*100
Star_Rating_final_general1[,c(4)] <- Star_Rating_final_general1[,c(4)]*2*100
Star_Rating_final_general1[,c(5)] <- Star_Rating_final_general1[,c(5)]*5*100
Star_Rating_final_general1[,c(6)] <- Star_Rating_final_general1[,c(6)]*(100/2)
Star_Rating_final_general1[,c(7)] <- Star_Rating_final_general1[,c(7)]*(3/100)
Star_Rating_final_general1[,c(8)] <- Star_Rating_final_general1[,c(8)]*10

```



Here we export all the data as .CSV file to to be used by the Shiny R application we made
```{r}
write.csv(final,"final.csv", row.names = TRUE)
write.csv(final_general,"final_general.csv", row.names = TRUE)
write.csv(Star_Rating_final,"Star_Rating_final.csv", row.names = TRUE)
write.csv(Star_Rating_final_general1,"Star_Rating_final_general.csv", row.names = TRUE)
```


```{r}
write.csv(cad_pivot1,"cad_p.csv",row.names = FALSE)
write.csv(hai_pivot1,"hai_p.csv",row.names = FALSE)
write.csv(hcahps_pivot1,"hcahps_p.csv",row.names = FALSE)
write.csv(mhs_pivot1,"mhs_p.csv",row.names = FALSE)
write.csv(oie_pivot1,"oie_p.csv",row.names = FALSE)
write.csv(pvc_pivot1,"pvc_p.csv",row.names = FALSE)
write.csv(tec_pivot1,"tec_p.csv",row.names = FALSE)

```

```{r}
write.csv(cad_uni,"cad_u.csv",row.names = FALSE)
write.csv(hai_uni,"hai_u.csv",row.names = FALSE)
write.csv(hcahps_uni,"hcahps_u.csv",row.names = FALSE)
write.csv(mhs_uni,"mhs_u.csv",row.names = FALSE)
write.csv(oie_uni,"oie_u.csv",row.names = FALSE)
write.csv(pvc_uni,"pvc_u.csv",row.names = FALSE)
write.csv(tec_uni,"tec_u.csv",row.names = FALSE)
```

```{r}
write.csv(cad_agg,"cad_a.csv",row.names = FALSE)
write.csv(hai_agg,"hai_a.csv",row.names = FALSE)
write.csv(hcahps_agg,"hcahps_a.csv",row.names = FALSE)
write.csv(mhs_agg,"mhs_a.csv",row.names = FALSE)
write.csv(oie_agg,"oie_a.csv",row.names = FALSE)
write.csv(pvc_agg,"pvc_a.csv",row.names = FALSE)
write.csv(tec_agg,"tec_a.csv",row.names = FALSE)
```


END